---
title: "Untitled"
author: "Matthew Copeland"
date: "February 13, 2019"
output: html_document
---

```{r}
# Load tidyverse
library(tidyverse)

# Load and view the data
milk <- read.csv("state_milk_production.csv")
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
## Kelsey McKenna Individual
mean1997 <- milk %>%
  filter(year == 1997) %>% summarize(mean(milk_million))
mean1997
med1997 <- milk %>%
  filter(year == 1997) %>% summarize(median(milk_million))
med1997
max1997 <- milk %>%
  filter(year == 1997) %>% summarize(max(milk_million))
max1997
min1997 <- milk %>%
  filter(year == 1997) %>% summarize(min(milk_million))
min1997

```
### Kelsey McKenna 1997
For my birth year of 1997 there the mean is 3121.82 millions of pounds of milk produced per state, the median is 1436 millions of pounds per state, the maximum amount of milk a state produced this year was 27,582 million pounds and the minimum produced was 15 million pounds. 

## Shreeya Basrur Individual
```{r}
milk <- read.csv("state_milk_production.csv")
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
mean1999 <- milk %>%
  filter(year == 1999) %>% summarize(mean(milk_million))
mean1999
med1999 <- milk %>%
  filter(year == 1999) %>% summarize(median(milk_million))
med1999
max1999 <- milk %>%
  filter(year == 1999) %>% summarize(max(milk_million))
max1999
min1999 <- milk %>%
  filter(year == 1999) %>% summarize(min(milk_million))
min1999

```
### Shreeya Basrur
For my birth year, the mean was 3251.8 millions of pounds and the median was 1418 million pounds.The minimum production was 14 million pounds and the maximum production was 30,444 pounds.

## James Burke Individual
```{r}
milk <- read.csv("state_milk_production.csv")
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
mean1999 <- milk %>%
  filter(year == 1999) %>% summarize(mean(milk_million))
mean1999
med1999 <- milk %>%
  filter(year == 1999) %>% summarize(median(milk_million))
med1999
max1999 <- milk %>%
  filter(year == 1999) %>% summarize(max(milk_million))
max1999
min1999 <- milk %>%
  filter(year == 1999) %>% summarize(min(milk_million))
min1999

```
### James Burke
For my birth year, the mean was 3251.8 millions of pounds and the median was 1418 million pounds.The minimum production was 14 million pounds and the maximum production was 30,444 pounds.

## Matthew Copeland Individual
```{r}
milk <- read.csv("state_milk_production.csv")
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
mean1998 <- milk %>%
  filter(year == 1998) %>% summarize(mean(milk_million))
mean1998
med1998 <- milk %>%
  filter(year == 1998) %>% summarize(median(milk_million))
med1998
max1998 <- milk %>%
  filter(year == 1998) %>% summarize(max(milk_million))
max1998
min1998 <- milk %>%
  filter(year == 1998) %>% summarize(min(milk_million))
min1998

```
### Matthew Copeland
For my birth year, the mean was 3145.22 millions of pounds and the median was 1411.5 million pounds.The minimum production was 14 million pounds and the maximum production was 27,620 pounds.

#Team Work
```{r}
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
milksub <- milk %>%
  filter(state %in% c('Colorado','Maryland','California','New York','Florida')) %>%
  select(state, year, milk_million)

ggplot(data = milksub, aes(x = year, y = milk_million, color = state)) +
  geom_point() + 
  geom_smooth() +
  ggtitle('Pounds of Milk Over Time by State') +
  xlab('Year') +
  ylab('Milk Produced (Million lb)')
```
## Plot Explained
This plot shows that back in 1970 California and New York started out producing the most milk, but then California increase their milk production by a lot in comparison to the other states. The other states we picked didn't produce much milk in comparison, but increase their production a bit.

```{r}
yearmilk <- milk %>%
  group_by(year) %>% summarize(max(milk_million))
yearmilk

```